Analysis for Project

### 2021-11-17 analysis/analysis.Rmd

```{r calc-cond-means, warning=FALSE}
coef_table_mod0 <- calculate_cond_means(model0)
```

@@

```{r cond-means-model4, warning=FALSE}
coef_table_mod4 <- calculate_cond_means(model4)

@@

```{r cond-means-model-compare, fig.height=12, warning=FALSE}
#calculate remaining marginal means
coef_table_mod1 <- calculate_cond_means(model1)
coef_table_mod2 <- calculate_cond_means(model2)

>>>>

```{r calc-cond-means, warning=FALSE}
coef_table_mod0 <- calculate_marg_means(model0)
```

@@

```{r cond-means-model4, warning=FALSE}
coef_table_mod4 <- calculate_marg_means(model4)

@@

```{r cond-means-model-compare, fig.height=12, warning=FALSE}
#calculate remaining marginal means
coef_table_mod1 <- calculate_marg_means(model1)
coef_table_mod2 <- calculate_marg_means(model2)
